Structural controllability of ecological networks

### 2018-06-28 paper/supp-info.Rmd
Explain changes of delta in supp info
#50

We follow @rohr_structural_2014 and @saavedra_nested_2016 to calculate the structural stability of the empirical networks. 
We first calculate the stability condition $\hat{\gamma}$ using all species in the network. 
To simplify the calculations we assumed that there is no mutualistic trade-off, and a mean field interspecific competition of $\rho = 0.005$ [@saavedra_nested_2016]. 
To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural feasibility $\Omega$ for a level of mutualism equal to the stability condition found previously. 
The choice of the parameters, specifically the interspecific competition $\rho$ had only a small impact on the relative contribution of species to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)a).

In addition, the interspecific competition had a minor impact on our result that indicates that critical species (those with $\phi = 1$) have a larger than average contribution to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)b).

>>>>

We follow @rohr_structural_2014 and @saavedra_nested_2016 to calculate the structural stability of the empirical networks. 
We first calculate the stability condition $\hat{\gamma}$ using all species in the network. 
To calculate the contribution to stable coexistence of a given species, we removed the focal species from the network and then calculated the corresponding structural stability $\Omega$ for a level of mutualism equal to the stability condition found previously. 
For simplicity, in the main text we show results for when there was no mutualistic trade-off $\delta = 0$ and an intermediate value of interspecific competition of $\rho = `r drake::readd(chosen_rho)`$ [@saavedra_nested_2016]. 
The choice of the parameters had only a minor impact on the relative contribution of species to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)a) and overall there was no change on our result that indicates that critical species (those with $\phi = 1$) have a larger than average contribution to stable coexistence (Figure \@ref(fig:fig-rho-sensitivity)b).
